Upper limits on CN from exocomets transiting $\beta$~Pictoris

### 2025-04-11 src/tex/ms.tex
final tweaks

\documentclass{aa}  
\usepackage{rotating}
\usepackage{natbib}
\usepackage{amsmath}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style

@@

   \keywords{comets --- transits, spectroscopy}

@@

The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES).
%
The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
%
Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
%
This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin. This binned ratio was then fitted using a second order polynomial.
%
The original spectrum was finally divided by this polynomial to correct for the changes.

@@

%For both HARPS and UVES w
We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}).
%
%For HARPS
This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
        \caption{Plot of the stacked spectrum in the comet rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange. The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_comet_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

@@

>>>>

\documentclass{aa}  
\usepackage{rotating}
\usepackage{natbib}
\usepackage{amsmath}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
\usepackage{float}
\usepackage{placeins}

@@

   \keywords{comets --- transits, spectroscopy, stars: individual: Beta Pictoris}

@@

The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES).
%
The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
%
Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
%
This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin, {\bf clipping points more than 2.7 Median Absolute Deviations (MAD) away from the median of each bin.} This binned ratio was then fitted using a second order polynomial.
%
The original spectrum was finally divided by this polynomial to correct for the changes.

@@

%For both HARPS and UVES w
We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), {\bf similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.}
%
%For HARPS
This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
        \caption{{\bf Similar to Figure~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the cometp.} The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_comet_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

@@

\clearpage
\FloatBarrier
